Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
reviewed 3.4 Safety specifications for dynamical systems

@@

As mentioned earlier, 
in this work we are not bound to the synthesis of digital stabilizing controllers -- 
a well known task in the literature on digital control system -- 
but target safety requirements with an overall approach that is sound and automated. 
More specifically, 
we require that the closed-loop system \eqref{eq:closedloopss} meets given safety specifications. 
A safety specification raises a requirement on the states of the model, 
such that the feedback controller (namely the choice of the gains in $K$) 
must ensure that the states never exist such requirement. 
Note that a stable, closed-loop system is not necessarily a safe system: 
indeed, the state values may leave the safe whilst they converge to the equilibrium, 
which is typical in the case of oscillatory dynamics. However, a safe system will always be stable.

In this work, the safety property represented by $\phi_{safety}$ is encoded as follows: 
%
\begin{equation}
\label{eq:safetyliteral}
\phi_{safety}\iff \forall k\geq 0, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
\end{equation}
%
%\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th instant, respectively. 
This means that the states will always be within the $n$-dimensional hyper-box. 
%, which is typically defined by the safety specification.

Furthermore, 
it is practically relevant to consider constraints on the input signal $u_{k}$, 
which we assume has given bounds $\overline{u}$ and $\underline{u}$, 
such that ${\underline{u} \leq u_{k} \leq \overline{u}},\forall k\geq 0$.  
In practice, 
this means that the control input saturates in view of physical constraints.

@@

\begin{proof} 
Consider the set of initial states, $X_0$, assumed to be convex since it's a hypercube. 
Name $v_i$ its vertexes, where $i=1,\ldots, 2^n$.  
Thus any point $x \in X_0$ can be expressed by convexity as $x = \sum_{i=1}^{2^n} \alpha_i v_i$, 
where $\sum_{i=1}^{2^n} \alpha_i =1$. \\
So then if $x_0=x$, then 
\begin{align*}
x_k   &= (A_d - B_d K)^k x \\
      &= (A_d - B_d K)^k \sum_{i=1}^{2^n} \alpha_i v_i \\
      &= \sum_{i=1}^{2^n} \alpha_i (A_d - B_d K)^k v_i \\
      &= \sum_{i=1}^{2^n} \alpha_i x_k^i
 \end{align*}     
where $x_k^i$ denotes the trajectories obtained from the single vertexes $v_i$. 
\end{proof}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=0.7\textwidth]{ct.eps}
\vspace{0.1cm}
\caption{Completeness threshold}
\end{figure*}

>>>>

\todo{Have we covered all the literature by Feron et al?}

@@

In this study, we are not bound to the synthesis of digital stabilizing controllers -- 
a well known task in the literature on digital control system -- 
but target safety requirements with an overall approach that is sound and automated. 
More specifically, 
we require that the closed-loop system \eqref{eq:closedloopss} meets given safety specifications. 
A safety specification raises a requirement on the states of the model, 
such that the feedback controller (namely the choice of the gains in $K$) 
must ensure that the states never exist such requirement. 
Note that a stable, closed-loop system is not necessarily a safe system: 
indeed, the state values may leave the safe whilst they converge to the equilibrium, 
which is typical in the case of oscillatory dynamics. However, a safe system will always be stable.
In this work, the safety property represented by $\phi_{safety}$ is encoded as follows: 
%
\begin{equation}
\label{eq:safetyliteral}
\phi_{safety}\iff \forall k\geq 0, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
\end{equation}
%
%\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th instant, respectively. 
This means that the states will always be within the $n$-dimensional hyper-box. 
%, which is typically defined by the safety specification.

Furthermore, 
it is practically relevant to consider constraints on the input signal $u_{k}$, 
which we assume has given bounds $\overline{u}$ and $\underline{u}$, 
such that ${\underline{u} \leq u_{k} \leq \overline{u}},\forall k\geq 0$.  
This means that the control input saturates in view of physical constraints.

@@

\begin{proof} 
Consider the set of initial states, $X_0$, assumed to be convex since it's a hypercube. 
Name $v_i$ its vertexes, where $i=1,\ldots, 2^n$.  
Thus any point $x \in X_0$ can be expressed by convexity as $x = \sum_{i=1}^{2^n} \alpha_i v_i$, 
where $\sum_{i=1}^{2^n} \alpha_i =1$. \\
So then if $x_0=x$, then 
\begin{align*}
x_k   &= (A_d - B_d K)^k x = (A_d - B_d K)^k \sum_{i=1}^{2^n} \alpha_i v_i \\
      &= \sum_{i=1}^{2^n} \alpha_i (A_d - B_d K)^k v_i = \sum_{i=1}^{2^n} \alpha_i x_k^i, 
 \end{align*}     
where $x_k^i$ denotes the trajectories obtained from the single vertexes $v_i$. 
\end{proof}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=0.7\textwidth]{ct.eps}
\vspace{0.1cm}
\caption{Completeness threshold for multi-staged verification}
\end{figure*}
